---
output:
  pdf_document:
    keep_tex: true
    fig_caption: yes
    latex_engine: pdflatex
    template: svm-latex-syllabus.tex
geometry: margin=0.85in

title: "INR 5000: International Relations Core Seminar | Reading List"
author: "Lecturer: Joshua Scriven"
date: "Fall 2017"

email: "jscriven@fsu.edu"
web: "github.com/joshuascriven"
officehours: "W 09:00-11:30"
office: "233 Bellamy Building"
classroom: "*133*"
classhours: "TR 11:45-14:30 p.m."

fontfamily: mathpazo
fontsize: 10pt
header-includes:
   - \linespread{1.05}
---


```{r loadpacks, echo = FALSE}
library(RefManageR)
library(rio)
```

```{r userinput, echo = FALSE}
bibloc <- "bibfile.bib"
day0 <- "2017-08-15"
unit <- "Week "
topicsIN <- import("topics.csv")
topics <- c(
            ": What is International Relations? How is it Evaluated?",
            ": Anarchy and the Paradigms",
            ": The State",
            ": Domestic Politics and Institutions",
            ": Transnational and Non-State Actors",
            ": Strategic Choice Approach",
            ": Interstate Conflict",
            ": Civil Conflict",
            ": Conflict Duration & Resolution",
            ": International Institutions: Design",
            ": International Institutions: Compliance, Influence, and Enforcement",
            ": International Institutions: Human Rights Regime",
            ": International Political Economy: Trade and Foreign Direct Investment",
            ": International Political Economy: International Finance and Foreign Aid",
            ": International Political Economy: Migration",
            ": Economic Sanctions",
            ": The Democratic Peace",
            ": Politics of the Environment"
            )
```

```{r date, echo = FALSE}
mon <- as.Date(day0)

advdate <- function(obj, adv) {
 tmon <- obj + 7*(adv-1)
 tfri <- obj + 4 + 7*(adv-1)
 tmon <- format(tmon, format="%m/%d")
 tfri <- format(tfri, format="%m/%d")
 zadv <- sprintf("%02d", adv)
 tmp <- paste(unit,zadv,sep='',", ", tmon," - ",tfri)
 return(tmp)
}
```

```{r makebib, echo = FALSE}
bib <- ReadBib(bibloc) # Change to whatever is your .bib file
myopts <- BibOptions(bib.style = "authoryear", style="latex", first.inits=F, max.names = 20, no.print.fields = c("doi"), sorting = "nyt")
```

<!-- main section for modification -->

```{r refsSupsLists, echo = FALSE}
refs <- vector("list", 20)
for(i in 1:(max(topicsIN$week,na.rm=T))){
  refs[[i]] <-as.character(subset(topicsIN, type=="refs" & week==i)$cite)
}
sups <- vector("list", 20)
for(i in 1:(max(topicsIN$week,na.rm=T))){
  sups[[i]] <-as.character(subset(topicsIN, type=="sups" & week==i)$cite)
}

```

<!-- The remainder of the code will compile & print weekly reading lists (after inserted topics) -->

# Required Readings

\Urlmuskip=0mu plus 2mu

`r j = 1`
##  `r advdate(mon, j)``r paste(topics[j],"|",length(refs[[j]]), "Readings")`


```{r, echo = FALSE, results="asis"}
if (length(refs[[j]])!=0) {
  bib[refs[[j]]]
}
```

### Supplementary `r paste("|",length(sups[[j]]), "Readings")`:
```{r, echo = FALSE, results="asis"}
if (length(sups[[j]])!=0) {
  bib[sups[[j]]]
}
```

`r j = j+1`
##  `r advdate(mon, j)``r paste(topics[j],"|",length(refs[[j]]), "Readings")`
```{r, echo = FALSE, results="asis"}
if (length(refs[[j]])!=0) {
  bib[refs[[j]]]
}
```

### Supplementary `r paste("|",length(sups[[j]]), "Readings")`:
```{r, echo = FALSE, results="asis"}
if (length(sups[[j]])!=0) {
  bib[sups[[j]]]
}
```


`r j = j+1`
##  `r advdate(mon, j)``r paste(topics[j],"|",length(refs[[j]]), "Readings")`
```{r, echo = FALSE, results="asis"}
if (length(refs[[j]])!=0) {
  bib[refs[[j]]]
}
```


### Supplementary `r paste("|",length(sups[[j]]), "Readings")`:
```{r, echo = FALSE, results="asis"}
if (length(sups[[j]])!=0) {
  bib[sups[[j]]]
}
```


`r j = j+1`
##  `r advdate(mon, j)``r paste(topics[j],"|",length(refs[[j]]), "Readings")`
```{r, echo = FALSE, results="asis"}
if (length(refs[[j]])!=0) {
  bib[refs[[j]]]
}
```

### Supplementary `r paste("|",length(sups[[j]]), "Readings")`:
```{r, echo = FALSE, results="asis"}
if (length(sups[[j]])!=0) {
  bib[sups[[j]]]
}
```


`r j = j+1`
##  `r advdate(mon, j)``r paste(topics[j],"|",length(refs[[j]]), "Readings")`
```{r, echo = FALSE, results="asis"}
if (length(refs[[j]])!=0) {
  bib[refs[[j]]]
}
```

### Supplementary `r paste("|",length(sups[[j]]), "Readings")`:
```{r, echo = FALSE, results="asis"}
if (length(sups[[j]])!=0) {
  bib[sups[[j]]]
}
```


`r j = j+1`
##  `r advdate(mon, j)``r paste(topics[j],"|",length(refs[[j]]), "Readings")`
```{r, echo = FALSE, results="asis"}
if (length(refs[[j]])!=0) {
  bib[refs[[j]]]
}
```

### Supplementary `r paste("|",length(sups[[j]]), "Readings")`:
```{r, echo = FALSE, results="asis"}
if (length(sups[[j]])!=0) {
  bib[sups[[j]]]
}
```


`r j = j+1`
##  `r advdate(mon, j)``r paste(topics[j],"|",length(refs[[j]]), "Readings")`
```{r, echo = FALSE, results="asis"}
if (length(refs[[j]])!=0) {
  bib[refs[[j]]]
}
```

### Supplementary `r paste("|",length(sups[[j]]), "Readings")`:
```{r, echo = FALSE, results="asis"}
if (length(sups[[j]])!=0) {
  bib[sups[[j]]]
}
```


`r j = j+1`
##  `r advdate(mon, j)``r paste(topics[j],"|",length(refs[[j]]), "Readings")`
```{r, echo = FALSE, results="asis"}
if (length(refs[[j]])!=0) {
  bib[refs[[j]]]
}
```

### Supplementary `r paste("|",length(sups[[j]]), "Readings")`:
```{r, echo = FALSE, results="asis"}
if (length(sups[[j]])!=0) {
  bib[sups[[j]]]
}
```


`r j = j+1`
##  `r advdate(mon, j)``r paste(topics[j],"|",length(refs[[j]]), "Readings")`
```{r, echo = FALSE, results="asis"}
if (length(refs[[j]])!=0) {
  bib[refs[[j]]]
}
```

### Supplementary `r paste("|",length(sups[[j]]), "Readings")`:
```{r, echo = FALSE, results="asis"}
if (length(sups[[j]])!=0) {
  bib[sups[[j]]]
}
```


`r j = j+1`
##  `r advdate(mon, j)``r paste(topics[j],"|",length(refs[[j]]), "Readings")`
```{r, echo = FALSE, results="asis"}
if (length(refs[[j]])!=0) {
  bib[refs[[j]]]
}
```

### Supplementary `r paste("|",length(sups[[j]]), "Readings")`:
```{r, echo = FALSE, results="asis"}
if (length(sups[[j]])!=0) {
  bib[sups[[j]]]
}
```


`r j = j+1`
##  `r advdate(mon, j)``r paste(topics[j],"|",length(refs[[j]]), "Readings")`
```{r, echo = FALSE, results="asis"}
if (length(refs[[j]])!=0) {
  bib[refs[[j]]]
}
```

### Supplementary `r paste("|",length(sups[[j]]), "Readings")`:
```{r, echo = FALSE, results="asis"}
if (length(sups[[j]])!=0) {
  bib[sups[[j]]]
}
```


`r j = j+1`
##  `r advdate(mon, j)``r paste(topics[j],"|",length(refs[[j]]), "Readings")`
```{r, echo = FALSE, results="asis"}
if (length(refs[[j]])!=0) {
  bib[refs[[j]]]
}
```

### Supplementary `r paste("|",length(sups[[j]]), "Readings")`:
```{r, echo = FALSE, results="asis"}
if (length(sups[[j]])!=0) {
  bib[sups[[j]]]
}
```


`r j = j+1`
##  `r advdate(mon, j)``r paste(topics[j],"|",length(refs[[j]]), "Readings")`
```{r, echo = FALSE, results="asis"}
if (length(refs[[j]])!=0) {
  bib[refs[[j]]]
}
```

### Supplementary `r paste("|",length(sups[[j]]), "Readings")`:
```{r, echo = FALSE, results="asis"}
if (length(sups[[j]])!=0) {
  bib[sups[[j]]]
}
```


`r j = j+1`
##  `r advdate(mon, j)``r paste(topics[j],"|",length(refs[[j]]), "Readings")`
```{r, echo = FALSE, results="asis"}
if (length(refs[[j]])!=0) {
  bib[refs[[j]]]
}
```

### Supplementary `r paste("|",length(sups[[j]]), "Readings")`:
```{r, echo = FALSE, results="asis"}
if (length(sups[[j]])!=0) {
  bib[sups[[j]]]
}
```


`r j = j+1`
##  `r advdate(mon, j)``r paste(topics[j],"|",length(refs[[j]]), "Readings")`
```{r, echo = FALSE, results="asis"}
if (length(refs[[j]])!=0) {
  bib[refs[[j]]]
}
```

### Supplementary `r paste("|",length(sups[[j]]), "Readings")`:
```{r, echo = FALSE, results="asis"}
if (length(sups[[j]])!=0) {
  bib[sups[[j]]]
}
```
