\documentclass[10pt,]{article}
\usepackage[margin=0.85in]{geometry}
\usepackage[hyphens]{url}
\usepackage{float, bbding}
\usepackage{wrapfig}
\newcommand*{\authorfont}{\fontfamily{phv}\selectfont}
\usepackage[]{mathpazo}
\usepackage{abstract}
\renewcommand{\abstractname}{}    % clear the title
\renewcommand{\absnamepos}{empty} % originally center
\newcommand{\blankline}{\quad\pagebreak[2]}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{longtable,booktabs}

\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{6pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{6pt plus 2pt minus 2pt}

\titleformat*{\subsubsection}{\normalsize\itshape}

\usepackage{titling}
\setlength{\droptitle}{-.25cm}

%\setlength{\parindent}{0pt}
%\setlength{\parskip}{6pt plus 2pt minus 1pt}
%\setlength{\emergencystretch}{3em}  % prevent overfull lines

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{lastpage}
\renewcommand{\headrulewidth}{0.3pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{\footnotesize INR3933: Politics of International Law \textbar{} (Covid) Syllabus -- Summer B 2020}
\lfoot{}
\cfoot{\small \thepage/\pageref*{LastPage}}
\rfoot{}

\fancypagestyle{firststyle}
{
\renewcommand{\headrulewidth}{0pt}%
   \fancyhf{}
   \fancyfoot[C]{\small \thepage/\pageref*{LastPage}}
}

%\def\labelitemi{--}
%\usepackage{enumitem}
%\setitemize[0]{leftmargin=25pt}
%\setenumerate[0]{leftmargin=25pt}


\makeatletter
\@ifpackageloaded{hyperref}{}{%
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
}
\@ifpackageloaded{xcolor}{
    \PassOptionsToPackage{usenames,dvipsnames}{xcolor}
}{%
    \usepackage[usenames,dvipsnames]{xcolor}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={ ()},
            pdfkeywords = {},
            pdftitle={INR3933: Politics of International Law \textbar{} (Covid) Syllabus},
            colorlinks=true,
            citecolor=Sepia,
            urlcolor=Sepia,
            linkcolor=Sepia,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls


\setcounter{secnumdepth}{0}

\usepackage{longtable}




\usepackage{setspace}

\title{INR3933: Politics of International Law \textbar{} (Covid) Syllabus}
\author{Lecturer: Joshua Scriven}
\date{Summer B 2020}


%%%%% tables that span multiple pages
\usepackage{longtable}

%%%%color in tables
\usepackage{xcolor,colortbl}

%%%%for resizing tables
\usepackage{adjustbox}

\newcommand{\mc}[2]{\multicolumn{#1}{c}{#2}}
\definecolor{Gray}{gray}{0.85}
\definecolor{LightCyan}{rgb}{0.88,1,1}


\begin{document}

		\maketitle
	

		\thispagestyle{firststyle}

\begin{center}
\begin{tabular}{llccll}
\hline
\rowcolor{Gray}
Instructor: & Joshua Scriven &          \hspace{3cm}           &
Email: & \href{mailto:jscriven@fsu.edu}{\nolinkurl{jscriven@fsu.edu}}\\

Classroom: &  \href{https://fsu.zoom.us/meeting}{Online} & &
Class Time: & M--F 11:00--12:15\\
Office: & \href{https://fsu.zoom.us/meeting}{Online} & &
Office Hours: & MW 12:30--13:45\\
\hline
\end{tabular}

\begin{minipage}{5.2in}
  \begin{flushleft}
    {\color{Gray}{\RectangleBold}} ~{\footnotesize ``{[}T{]}he blood of millions of men, numberless and unprecedented
sufferings, useless slaughter and frightful ruin, are the sanction of
the covenant which unites you in a solemn pledge which must change the
future history of the world.'' --Address of his Holiness Pope Paul VI to the United Nations (Oct.~4,
1965)}\newline
  \end{flushleft}
\end{minipage}


\end{center}

\vspace{2mm}


\hypertarget{course-description}{%
\section{Course Description}\label{course-description}}

In this course, students will use a combination of prerecorded lectures,
tutorial sessions, group presentations, short quizzes, and an
interactive simulation to cover topics in interntional law (IL)
distributed across four modules:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  What is international law and where is it found?
\item
  Actors in international law: who takes part?
\item
  When does international law apply?
\item
  How is international law applied?
\end{enumerate}

\hypertarget{learning-objectives}{%
\section{Learning Objectives}\label{learning-objectives}}

This one-semester course is intended to:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  introduce the fundamentals of IL and its relationship with domestic
  law;
\item
  improve your understanding of the role of IL and international
  organizations;
\item
  familiarize you with the legal principles governing the creation,
  rights, and duties of subjects of IL;
\item
  help you analyze the interplay of legal customs, and norms which
  govern diplomacy and treaties;
\item
  examine circumstances where law is absent or deficient in maintaining
  stability and peaceful interactions;
\item
  discuss whether IL has been beneficial to the human and global
  environment.
\end{enumerate}

\hypertarget{required-textbook}{%
\section{Required Textbook}\label{required-textbook}}

Dixon, Martin, Robert McCorquodale, and Sarah (2011).
\emph{Cases and materials on international law}. Oxford University
Press.

\hypertarget{covid-related-adjustments}{%
\section{Covid-related Adjustments}\label{covid-related-adjustments}}

This accelerated 6-week course was originally designed for in-person
classroom meetings five (5) days a week, but will now be delivered
online without daily meetings. I have sought to incorporate features of
both synchronous (live) and asynchronous (delayed) interaction to best
facilitate learning, while accounting for the special circumstances
students might now face. If a student needs additional accomodations,
this should be indicated \textbf{in writing} within the first 2 weeks of
the semester. All links to external sites such as zoom, office
appointments, can be found on the Canvas homepage.

\newpage

\hypertarget{grades}{%
\section{Grades}\label{grades}}

\hypertarget{composition}{%
\subsection{Composition}\label{composition}}

Your final course grade is a combination of scores according to the
table shown here. Additional explanations for each component can be
found on the \emph{Assignments} tab on Canvas.

\hypertarget{quizzes-final-exam}{%
\subsubsection{Quizzes \& Final Exam}\label{quizzes-final-exam}}

Each module has a short quiz which can be completed at any time before
the final day of the semester. Quizzes and the final exam are open-book.
The Final is completed as a group assesment with a single answer sheet
is submitted per group, along with and evaluations of each other's
contribution.

\hypertarget{group-presentation}{%
\subsubsection{Group Presentation}\label{group-presentation}}

Each class group must present on an approved topic of significance to
contemporary international legal and political discourse.

\hypertarget{simulation-grades}{%
\subsubsection{Simulation Grades}\label{simulation-grades}}

Each student is given both a individual grade for a research paper and a
grade shared by every member of their group for the practical, in-class
portion of the exercise.

\hypertarget{tutorial-guides-discussion}{%
\subsubsection{Tutorial Guides \&
Discussion}\label{tutorial-guides-discussion}}

Each module has a tutorial session, where students must submit topics
beforehand which influence the direction of discussions and quizzes for
that module. For each discussion, students must engage each other during
the live session. An alternative assignment is available. Students
contributions are evaluated by both the professor and fellow group
members.

\hypertarget{scales}{%
\subsection{Scales}\label{scales}}

This course uses the grading scale displayed here. Due dates are rare,
but when they do exist, they should be adhered to. Assignments will
receive a deduction of 5 percent for each day they are late (i.e.,
SMTWRFA). Students are expected to complete missing assignments before
seeking any extra credit (offered to the entire class). Extra credit
will not be assigned within the last two weeks of the semester.

\begin{table}[!h]
\caption{\label{tab:unnamed-chunk-3}Grade Composition and Grading Scale}

\centering
\begin{tabular}[t]{ll}
\toprule
Component & Proportion\\
\midrule
Quizzes & 20\%\\
 & \\
Final & 20\%\\
Group Presentation & 20\%\\
Simulation (Group) & 15\%\\
\addlinespace
Simulation (Individual) & 10\%\\
Tutorial Guides & 5\%\\
Tutorial Discussion & 10\%\\
 & 0\%\\
Total & 100\%\\
\bottomrule
\end{tabular}
\centering
\begin{tabular}[t]{llllll}
\toprule
Grade & Range & Grade.1 & Range.1 & Grade.2 & Range.2\\
\midrule
 &  & A & >92\% & A- & 90\%-92\%\\
B+ & 87\%-89\% & B & 83\%-86\% & B- & 80\%-82\%\\
C+ & 77\%-79\% & C & 73\%-76\% & C- & 70\%-72\%\\
D+ & 67\%-69\% & D & 63\%-66\% & D- & 60\%-62\%\\
F & <60\% &  &  &  & \\
\bottomrule
\end{tabular}
\end{table}

\newpage

\hypertarget{course-policies}{%
\section{Course Policies}\label{course-policies}}

\hypertarget{student-responsibility-highlights}{%
\subsection{Student Responsibility
Highlights}\label{student-responsibility-highlights}}

\begin{itemize}
\tightlist
\item
  Students should log on to Canvas at least once a day to check for
  course updates.
\item
  Student should review module readings and lectures before tutorial
  sessions.
\item
  Students should contribute equally to group work and identify
  classmates who do not.
\item
  Students will not disrespect each other's religious, cultural,
  political, or ideological beliefs.
\item
  Students will accept each other's right to reasonably debate
  religious, cultural, political, or ideological beliefs of any
  kind.\footnote{Here, a reasonable argument must present at least one
    statement for and one against your chosen point of view.}
\end{itemize}

\hypertarget{rules-for-online-interaction}{%
\subsection{Rules for Online
Interaction}\label{rules-for-online-interaction}}

\begin{itemize}
\tightlist
\item
  You should be fully dressed as if you were physically attending a
  university class.
\item
  Caring for dependents is \textbf{not} considered distracting. Should
  the need arise, you are allowed to have people or pets \textbf{quietly
  sit} with you during video-enabled Zoom meetings.
\item
  Keep microphones on mute, unless you are answering or offering a
  question.
\item
  Please use the nonverbal features available to you on Zoom, where
  possible.
\item
  You may also silently use gestures you would normally use in a
  physical classroom environment, such as raising your hand.
\item
  \textbf{Remember: sarcasm is fine; joke within reason; and sexual
  harassment is a thing. Our online communications might not be conveyed
  as positively as our in-class interactions might.}
\end{itemize}

\hypertarget{syllabus-change-policy}{%
\subsection{Syllabus Change Policy}\label{syllabus-change-policy}}

Except for changes that substantially affect implementation of the
evaluation (grading) statement, this syllabus is a guide for the course
and is subject to change with advance notice.

\hypertarget{university-policies}{%
\section{University Policies}\label{university-policies}}

\hypertarget{university-attendance-policy}{%
\subsection{University Attendance
Policy}\label{university-attendance-policy}}

I do not take attendance in this course. Excused absences include
documented illness, deaths in the family and other documented crises,
call to active military duty or jury duty, religious holy days, and
official University activities. These absences will be accommodated in a
way that does not arbitrarily penalize students who have a valid excuse.
Consideration will also be given to students whose dependent children
experience serious illness.

\hypertarget{academic-honor-policy}{%
\subsection{Academic Honor Policy}\label{academic-honor-policy}}

The Florida State University Academic Honor Policy outlines the
University's expectations for the integrity of students' academic work,
the procedures for resolving alleged violations of those expectations,
and the rights and responsibilities of students and faculty members
throughout the process. Students are responsible for reading the
Academic Honor Policy and for living up to their pledge to ``\ldots{}be
honest and truthful and\ldots{} {[}to{]} strive for personal and
institutional integrity at Florida State University.'' (For more details
see the FSU Academic Honor Policy and procedures for addressing alleged
violationsLinks to an external site..)

\hypertarget{americans-with-disabilities-act}{%
\subsection{Americans With Disabilities
Act}\label{americans-with-disabilities-act}}

Students with disabilities needing academic accommodation should (1)
register with and provide documentation to the Student Disability
Resource Center and (2) bring a letter to the instructor indicating the
need for accommodation and what type. Please note that instructors are
not allowed to provide classroom accommodation to a student until
appropriate verification from the Student Disability Resource Center has
been provided. This syllabus and other class materials are available in
alternative format upon request. For more information about services
available to FSU students with disabilities, contact the Student
Disability Resource Center (SDRC) 108 Student Services Building
\textbar{} Florida State University \textbar{} (850) 644-9566 (voice)
\textbar{} (850) 644-8504 (TDD) \textbar{} Email:
\href{mailto:sdrc@admin.fsu.edu}{\nolinkurl{sdrc@admin.fsu.edu}}

\newpage

\hypertarget{class-schedule-and-readings}{%
\section{Class Schedule and
Readings}\label{class-schedule-and-readings}}

The class schedule is found on the \emph{Syllabus} page on Canvas. They
correspond to the readings below.

\Urlmuskip=0mu plus 2mu

\hypertarget{module-01-0511---0515-nature-sources-1-readings}{%
\subsection{Module 01, 05/11 - 05/15 \textasciitilde{} Nature \& Sources
\textbar{} 1
Readings}\label{module-01-0511---0515-nature-sources-1-readings}}

Dixon, McCorquodale, Williams - Cases \& Materials on International Law
Chapters 1 \& 2

\hypertarget{cases-4-readings}{%
\subsubsection{Cases \textbar{} 4 Readings}\label{cases-4-readings}}

Military and Paramilitary Activities in and against Nicaragua (Nicaragua
v United States)\\
Paquete Habana\\
The Lotus\\
Maritime Delimitation and Territorial Questions Between Qatar and
Bahrain Case (Qatar v Bahrain)

\hypertarget{module-02-0518---0522-treaties-domestic-law-1-readings}{%
\subsection{Module 02, 05/18 - 05/22 \textasciitilde{} Treaties \&
Domestic Law \textbar{} 1
Readings}\label{module-02-0518---0522-treaties-domestic-law-1-readings}}

Dixon, McCorquodale, Williams - Cases \& Materials on International Law
Chapters 3 \& 4

\hypertarget{module-03-0525---0529-international-personality-3-readings}{%
\subsection{Module 03, 05/25 - 05/29 \textasciitilde{} International
Personality \textbar{} 3
Readings}\label{module-03-0525---0529-international-personality-3-readings}}

\href{https://www.youtube.com/watch?v=0ViSYjt-wGw}{Video: What are the
sources of International Law?}\\
Dixon, McCorquodale, Williams - Cases \& Materials on International Law
Chapters 5, 7 \& 8

Kolb, Robert (2014).
\emph{The Relationship between the International and the Municipal Legal Order: Reflections on the Decision no 238/2014 of the Italian Constitutional Court}.
\url{http://www.qil-qdi.org/relationship-international-municipal-legal-order-reflections-decision-no-2382014-italian-constitutional-court/}.

\hypertarget{cases-2-readings}{%
\subsubsection{Cases \textbar{} 2 Readings}\label{cases-2-readings}}

Trendtex Trading Corporation v Central Bank of Nigeria\\
North Sea Continental Shelf Cases (Federal Republic of Germany v
Denmark; FRG v The Netherlands)

\hypertarget{module-04-0601---0605-international-human-rights-law-1-readings}{%
\subsection{Module 04, 06/01 - 06/05 \textasciitilde{} International
Human Rights Law \textbar{} 1
Readings}\label{module-04-0601---0605-international-human-rights-law-1-readings}}

Dixon, McCorquodale, Williams - Cases \& Materials on International Law
Chapters 6

\hypertarget{module-05-0608---0612-responsibility-immunity-1-readings}{%
\subsection{Module 05, 06/08 - 06/12 \textasciitilde{} Responsibility \&
Immunity \textbar{} 1
Readings}\label{module-05-0608---0612-responsibility-immunity-1-readings}}

Dixon, McCorquodale, Williams - Cases \& Materials on International Law
Chapters 9 \& 11

\hypertarget{module-06-0615---0619-law-of-the-sea-1-readings}{%
\subsection{Module 06, 06/15 - 06/19 \textasciitilde{} Law of the Sea
\textbar{} 1
Readings}\label{module-06-0615---0619-law-of-the-sea-1-readings}}

Dixon, McCorquodale, Williams - Cases \& Materials on International Law
Chapters 10

\hypertarget{cases-5-readings}{%
\subsubsection{Cases \textbar{} 5 Readings}\label{cases-5-readings}}

\href{https://scholar.google.com/scholar_case?case=15997705832480823650}{Saudi
Arabia v. Nelson}\\
\href{https://scholar.google.com/scholar_case?case=12305885770783175808}{Verlinden
BV v. Central Bank of Nigeria}\\
\href{https://www.courtlistener.com/opinion/2502147/walters-v-industrial-and-commercial-bank-of-china/}{Walters
V. Industrial And Commercial Bank Of China}\\
\href{https://scholar.google.com/scholar_case?case=3908553268744923367}{Gleissner
V. Air China Airlines Limited}\\
Trendtex Trading Corporation v Central Bank of Nigeria

\hypertarget{module-07-0622---0626-international-economic-law-1-readings}{%
\subsection{Module 07, 06/22 - 06/26 \textasciitilde{} International
Economic law \textbar{} 1
Readings}\label{module-07-0622---0626-international-economic-law-1-readings}}

Dixon, McCorquodale, Williams - Cases \& Materials on International Law
Chapters 13

\hypertarget{module-08-0629---0703-international-criminal-law-1-readings}{%
\subsection{Module 08, 06/29 - 07/03 \textasciitilde{} International
Criminal Law \textbar{} 1
Readings}\label{module-08-0629---0703-international-criminal-law-1-readings}}

Dixon, McCorquodale, Williams - Cases \& Materials on International Law
Chapters 14

\hypertarget{module-09-0706---0710-the-use-of-force-collective-security-and-peacekeeping-1-readings}{%
\subsection{Module 09, 07/06 - 07/10 \textasciitilde{} The Use of Force,
Collective Security and Peacekeeping \textbar{} 1
Readings}\label{module-09-0706---0710-the-use-of-force-collective-security-and-peacekeeping-1-readings}}

Dixon, McCorquodale, Williams - Cases \& Materials on International Law
Chapters 15


\end{document}

\makeatletter
\def\@maketitle{%
  \newpage
%  \null
%  \vskip 2em%
%  \begin{center}%
  \let \footnote \thanks
    {\fontsize{18}{20}\selectfont\raggedright  \setlength{\parindent}{0pt} \@title \par}%
}
%\fi
\makeatother
